\sysfull

### 2018-08-07 paper/asplos19/systemdescription.tex
revisions of system description

\sys is a new programming and execution model for intermittent operation on \emph{small embedded energy-harvesting devices}. It addresses the challenges given in Section~\ref{sec:background} making task-based intermittent applications {\em programmable}, {\em efficient} and {\em portable}, introducing a new programming model and runtime software system that supports adaptive task-based execution. Fig.~\ref{fig:system_overview} shows an overview of \sys.

>>>>

\sys is a new programming and execution model that supports adaptive task-based execution and eliminates restructuring and re-compilation of applications considering device's energy buffer. \sys addresses the challenges given in Section~\ref{sec:background} by making task-based intermittent applications portable in the sense of different energy storage sizes, while keeping their execution efficient. Fig.~\ref{fig:system_overview} shows an overview of \sys.
